### 2012-06-01 FFI-Simulator/ffi-simulator.tex
added some text in ffi designe doc

\subsection{Using OpenGL only for the simulations?}

@@

Our original idea was to use OpenGL to produce depth-maps of the object and (optionally) the seafloor, and then use CUDA to compute how a sonar array would illuminate this scene. However, if we can treat sound as ``light'', we believe it to be better to use OpenGL simulate the entire scene and generate the required 2D views and perspectives of it. The advantage of doing ``everything'' in OpenGL is pretty obvious, we may then support whatever OpenGL supports with little extra effort. The gaming industry demands speed, so such a simulator should also be very fast.

@@

We propose using OpenGL to simulate the scene, and model the array as lightsources. This will make it unsuitable for simulating speckle and diffraction effects, but a ``simple'' simulator should probably not take such effects into account anyhow. Penetrable objects can be simulated in either case, although we are not sure whether the

>>>>

In addition we see that each approach shares the same initial steps. The risk of selecting a OpenGL-only implementation is therefore reduced, since a CUDA implementation for the middle step can be selected based on experience with the initial steps in OpenGL.

\subsection{Using only OpenGL for the simulator?}

@@

Our original idea was to use OpenGL to produce depth-maps of the object and (optionally) the seafloor, and then use CUDA to compute how a sonar array would illuminate this scene. However, if we can treat sound as ``light'', we believe it to be better to use OpenGL simulate the entire scene and generate the required 2D views and perspectives of it. The advantage of doing ``everything'' in OpenGL is pretty obvious, we may then support whatever OpenGL supports with little extra effort. The gaming industry demands speed, so such a simulator should also be very fast. A CUDA implementation will benefit from more flexibility when it comes to simulating sound propagation in a non-ideal medium, and translucent objects.  With more complex models both the code complexity and developing time will naturally increase. However, we expect that such features will be more realizable in CUDA than OpenGL.

@@

We propose using OpenGL to simulate the scene, and model the array as lightsources. This will make it unsuitable for simulating speckle and diffraction effects, but a "simple'' simulator should probably not take such effects into account anyhow. Penetrable objects can be simulated in either case, although we are not sure whether the OpenGL framework can support this with ease inside its framework limits. An OpenGL implementation will be highly portable, and believed to support the functionality need to generate a good enough template image.
